\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-12-04 exps.tex
Added a bar for the second delay stmt
updated the number in exps

The result of the upper bound relaxation with reduced WCRT is shown in
Figure~\ref{fig:graph2}.  The upper bounds for delay statements in
AECS/CD2 decreased by 11.81\%, while that for Motor example reduced from
7.54 to 8.05\%. This is expected since the amount of computation
required in control flow is less demanding than data and hence, breaking
the critical paths in Motor did not reduce WCRT as much as AECS/CD2.
Therefore, we can see from the result that the size of the relaxation
depends on how designers write their program as well as type of the
application (i.e. data or control dominated).

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00)};
			\addplot + [postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

>>>>

The result of the upper bound relaxation with reduced WCRT is shown in
Figure~\ref{fig:graph2}.  The upper bounds for delay statements in
AECS/CD2 decreased by 11.81\%, while that for Motor example reduced from
6.42 to 8.05\%. This is expected since the amount of computation
required in control flow is less demanding than data and hence, breaking
the critical paths in Motor did not reduce WCRT as much as AECS/CD2.
Therefore, we can see from the result that the size of the relaxation
depends on how designers write their program as well as type of the
application (i.e. data or control dominated).

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}
